Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-07-15 prop_letter.tex
prop_letter.tex 55e2cf6 Revert...

\begin{proof} Suppose there is a $\delta$-deterministic
  QIVPM\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$, we claim that the
  following QIVPM
  \nb$\bar{\mu}^{\textrm{D}}:\events\rightarrow\left\{
    \imposs,\necess\right\} $ is cryptodeterministic:
\begin{equation}
\bar{\mu}^{\textrm{D}}\left(P\right)=\begin{cases}
\imposs\,, & \textrm{ if }\bar{\mu}\left(P\right)\subseteq\left[0,\delta\right]\:;\\
\necess\,, & \textrm{ if }\bar{\mu}\left(P\right)\subseteq\left[1-\delta,1\right]\:.
\end{cases}
\end{equation}
However, since we know that there is no cryptodeterministic QIVPM,
$\bar{\mu}^{\textrm{D}}$ cannot exist and hence $\bar{\mu}$ cannot
exist.

@@

\begin{example}\label{ex:three-dimensional-three-value}
  Given a three-dimensional Hilbert space with an orthonormal basis
  $\left\{ \ket{0},\ket{1},\ket{2}\right\} $,  let
  $\mathscr{I}_{1}=\left\{ \necess,\imposs,\unknown\right\} $,
  $\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$,
  $\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$, and
\begin{subequations}
\begin{eqnarray}
 &  & \begin{aligned}\imposs & =\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})\\
 & =\bar{\mu}(\proj{\ps})=\bar{\mu}(\proj{\ps'})\,,
\end{aligned}
\\
 &  & \begin{aligned}\necess & =\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})\\
 & =\bar{\mu}(\mathbb{1}-\proj{\ps})=\bar{\mu}(\mathbb{1}-\proj{\ps'})\,,
\end{aligned}
\\
 &  & \unknown=\bar{\mu}(P)\qquad\textrm{otherwise.}
\end{eqnarray}
\end{subequations}
It is straightforward to verify that $\bar{\mu}$ is a QIVPM. Then we will
prove $\coreBorn\left(\bar{\mu},\events\right)$ is an empty set by
contradiction. Suppose there is a mixed
state\nb$\rho=\sum_{j=1}^{N}q_{j}\proj{\phi_{j}}\in\coreBorn\left(\bar{\mu},\events\right)$,
where $\sum_{j=1}^{N}q_{j}=1$ and $q_{j}>0$. Since $\mu_{\rho}^{\mathrm{B}}(P)\in\bar{\mu}(P)$
for any\nb$P$, the mixed state\nb$\rho$ must satisfy
\begin{equation}
\melem{0}{\rho}{0}=\melem{\ps}{\rho}{\ps}=\melem{\ps'}{\rho}{\ps'}=0
\end{equation}
which implies $\ip{\phi_{j}}{0}=\ip{\phi_{j}}{\ps}=\ip{\phi_{j}}{\ps'}=0$
for all $j$. However, the last equation never holds. 
Thus, there is no state consistent with the QIVPM on all 
projectors\nb$P\in\events$, so Gleason's theorem does not hold for at least this
example.
\end{example}

@@

It is now not difficult to verify that for any totally mixed
state\nb$\rho$ on a three-dimensional Hilbert space,
$\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}}$ is a
QIVPM. Furthemore, we have:
\begin{itemize}
\item If $\left\Vert \rho-\rho'\right\Vert \le1/\left(12n\right)$,
$\rho'\in\coreBorn\left(\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}},\events\right)$.
\item If $\rho'\in\coreBorn\left(\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}},\events\right)$,
then $\left\Vert \rho-\rho'\right\Vert \le1/n$.
\end{itemize}
In other words, for the states consistent with this QIVPM,
$\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}}$ will become closer and
closer to $\rho$ as $n$ goes to infinity. In the limiting case when
the intervals are infinitely precise, i.e.,
$\set{\left[x,x\right]}{x\in\left[0,1\right]}$, any QIVPM can be
recast as a real-valued one and will have a unique state consistent
with it on every projector when $d\ge3$.

>>>>

\begin{proof} Suppose there is a $\delta$-deterministic
  QIVPM\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$, we claim that the
  following function\nb$\bar{\mu}^{\textrm{D}}:\events\rightarrow\left\{
    \imposs,\necess\right\} $ is a cryptodeterministic QIVPM:
\begin{equation}
\bar{\mu}^{\textrm{D}}\left(P\right)=\begin{cases}
\imposs\,, & \textrm{ if }\bar{\mu}\left(P\right)\subseteq\left[0,\delta\right]\:;\\
\necess\,, & \textrm{ if }\bar{\mu}\left(P\right)\subseteq\left[1-\delta,1\right]\:.
\end{cases}
\end{equation}
However, since we know that there is no cryptodeterministic QIVPM,
$\bar{\mu}^{\textrm{D}}$ cannot exist and hence $\bar{\mu}$ cannot
exist.

@@

\begin{example}\label{ex:three-dimensional-three-value}
  Given a three-dimensional Hilbert space with an orthonormal basis
  $\left\{ \ket{0},\ket{1},\ket{2}\right\} $,  let
  $\mathscr{I}_{1}=\left\{ \necess,\imposs,\unknown\right\} $,
  $\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$,
  $\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$, and
\begin{subequations}
\begin{eqnarray}
 &  & \begin{aligned}\imposs & =\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})\\
 & =\bar{\mu}(\proj{\ps})=\bar{\mu}(\proj{\ps'})\,,
\end{aligned}
\\
 &  & \begin{aligned}\necess & =\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})\\
 & =\bar{\mu}(\mathbb{1}-\proj{\ps})=\bar{\mu}(\mathbb{1}-\proj{\ps'})\,,
\end{aligned}
\\
 &  & \unknown=\bar{\mu}(P)\qquad\textrm{otherwise.}
\end{eqnarray}
\end{subequations}
It is straightforward to verify that $\bar{\mu}$
is a QIVPM. Now let $S_{1}=\left\{ \proj{0},\proj{\ps}\right\} $.
Because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$, we have
$\mu_{\rho}^{\mathrm{B}}(\proj{0})=\mu_{\rho}^{\mathrm{B}}(\proj{\ps})=0$
for any mixed state\nb$\rho\in\coreBorn\left(\bar{\mu},S_{1}\right)$.
Hence, $\rho$ cannot be any state other than $\ket{2}$, the only
pure state orthogonal to both $\ket{0}$ and $\ket{\ps}$, and it
is easy to verify $\proj{2}$ is actually in $\coreBorn\left(\bar{\mu},S_{1}\right)$.
Similarly, let $S_{2}=\left\{ \proj{0},\proj{\ps'}\right\} $. We
have $\coreBorn\left(\bar{\mu},S_{2}\right)=\left\{ \proj{1}\right\} $.
Therefore, 
\begin{equation}
\coreBorn\left(\bar{\mu},\events\right)\subseteq\coreBorn\left(\bar{\mu},S_{1}\right)\cap\coreBorn\left(\bar{\mu},S_{2}\right)=\emptyset
\end{equation}
Thus, there is no state that is consistent with the QIVPM on all projectors\nb$\events$,
so Gleason's theorem does not hold for at least this example.
\end{example}

@@

It is now not difficult to verify that for any totally mixed
state\nb$\rho$ on a three-dimensional Hilbert space,
$\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}}$ is a
QIVPM. Furthemore, we have:
\begin{itemize}
\item If $\left\Vert \rho-\rho'\right\Vert \le1/\left(12n\right)$,
$\rho'\in\coreBorn\left(\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}},\events\right)$.
\item If $\rho'\in\coreBorn\left(\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}},\events\right)$,
then $\left\Vert \rho-\rho'\right\Vert \le1/n$.
\end{itemize}
In other words, for the states consistent with this QIVPM,
$\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}}$ will become closer and
closer to $\rho'$ as $n$ goes to infinity. In the limiting case when
the intervals are infinitely precise, i.e.,
$\set{\left[x,x\right]}{x\in\left[0,1\right]}$, any QIVPM can be
recast as a real-valued one and will have a unique state consistent
with it on every projector when $d\ge3$.
